Nail: A practical interface generator for data formats

### 2014-08-14 paper/osdi14/relwk.tex
Cite Fisher, DDL

Closely related work has been done in the field of data description languages, for example
PacketTypes~\cite{mccann2000packet} and DataScript~\cite{DataScript}. However, PacketTypes works
only as a parser, not as an output generator and implement a C-like structure model enhanced with
length fields and constraints. DataScript adds output generation and built-in support for offset
fields. However, these systems cannot handle complicated encodings such as compressed data, which
are supported by Nail's stream transforms. Many built-in features of these date description
languages, such as the various ways of encoding array size or length and offsets, can be expressed
by Nail transformations, keeping the core language itself smaller and increasing flexibility.

>>>>

Closely related work has been done in the field of data description languages, for example
PacketTypes~\cite{mccann2000packet} and DataScript~\cite{DataScript}. A broader overview of data
description languages can be found in~\cite{Fisher:700DDL} However, PacketTypes works
only as a parser, not as an output generator and implement a C-like structure model enhanced with
length fields and constraints. DataScript adds output generation and built-in support for offset
fields. However, these systems cannot handle complicated encodings such as compressed data, which
are supported by Nail's stream transforms. Many built-in features of these date description
languages, such as the various ways of encoding array size or length and offsets, can be expressed
by Nail transformations, keeping the core language itself smaller and increasing flexibility.
